Multi-Resolution Neural Field Estimation

### 2011-03-10 Multiresolution_framework/ltx/manuscript.tex
added emails to affiliatins (required by the journal)

\author{P. Aram, D.R. Freestone~\IEEEmembership{Graduate Student Member,~IEEE}, M. Dewar, K.Scerri~\IEEEmembership{Member,~IEEE}, D.B. Grayden~\IEEEmembership{Member,~IEEE,} and V. Kadirkamanathan~\IEEEmembership{Member,~IEEE} % <-this % stops a space
\thanks{P. Aram* and V. Kadirkamanathan are with the Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, S1 3JD, U.K. (e-mail:p.aram@sheffield.ac.uk; visakan@sheffield.ac.uk).}% <-this % stops a space
\thanks{D.\ R.\ Freestone and D.\ B.\ Grayden are with the Department
of Electrical and Electronic Engineering, The University of Melbourne, and The Bionic Ear Institute, VIC, Australia. The Bionic Ear Institute acknowledges the support it receives from the Victorian State Government through the Operational Infrastructure Support Program. (e-mail:dfreestone@bionicear.org; grayden@unimelb.edu.au).}
\thanks{M. Dewar is with the Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA. (e-mail:mike.dewar@columbia.edu).}
\thanks{K. Scerri is with the Department of Systems and Control Engineering, University
of Malta, Msida, Malta. (e-mail:kenneth.scerri@um.edu.mt).}}
% <-this % stops a space
%\thanks{Manuscript received April 19, 2005; revised January 11, 2007.}}

>>>>

\author{P. Aram, D.R. Freestone~\IEEEmembership{Graduate Student Member,~IEEE}, M. Dewar, K.Scerri~\IEEEmembership{Member,~IEEE}, D.B. Grayden~\IEEEmembership{Member,~IEEE,} and V. Kadirkamanathan~\IEEEmembership{Member,~IEEE} % <-this % stops a space
\thanks{P. Aram* and V. Kadirkamanathan are with the Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, S1 3JD, U.K. (e-mail:p.aram@sheffield.ac.uk; visakan@sheffield.ac.uk).}% <-this % stops a space
\thanks{D.\ R.\ Freestone and D.\ B.\ Grayden are with the Department
of Electrical and Electronic Engineering, The University of Melbourne, and The Bionic Ear Institute, VIC, Australia. (e-mail:dfreestone@bionicear.org; grayden@unimelb.edu.au). The Bionic Ear Institute acknowledges the support it receives from the Victorian State Government through the Operational Infrastructure Support Program.}
\thanks{M. Dewar is with the Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA. (e-mail:mike.dewar@columbia.edu).}
\thanks{K. Scerri is with the Department of Systems and Control Engineering, University
of Malta, Msida, Malta. (e-mail:kenneth.scerri@um.edu.mt).}}
% <-this % stops a space
%\thanks{Manuscript received April 19, 2005; revised January 11, 2007.}}
